\documentclass[11pt,a4paper]{article}

% --- Encoding cross-engine safe ---
\usepackage{iftex}
\ifPDFTeX
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
\fi

% --- Layout & links ---
\usepackage[margin=1.5in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,urlcolor=blue}
\usepackage{enumitem}

% --- Use local EB Garamond font ---
\usepackage{fontspec} % Para usar fuentes OpenType y TrueType
\setmainfont{EB Garamond}[
    UprightFont = * Regular,
    ItalicFont = * Italic,
    BoldFont = * SemiBold,
    BoldItalicFont = * SemiBold Italic,
]

% --- Justification ---
\usepackage{ragged2e}
\justifying

% --- Line spacing ---
\usepackage{setspace}
\setstretch{1.25}

% --- Paragraph spacing ---
\setlength{\parskip}{0.2em}

% --- Page layout ---
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
% Elegant header: course title left, document title center, page number right
\fancyhead[L]{\small\textsc{AI in Financial Services}}
% \fancyhead[C]{\small\textbf{LumenCash: Embedded Finance}}
\fancyhead[R]{\small\thepage}
\vspace{1em}
\renewcommand{\headrulewidth}{0.05pt}
% Optional: add a subtle footer with author or date
% \fancyfoot[C]{\scriptsize\textcolor{gray}{\today}}

% --- Do not number the first page ---
\thispagestyle{empty}


% --- Itemize settings ---
\setlist{nosep,leftmargin=*,labelsep=0.5em}

% --- Title ---

\begin{document}

\LARGE{\textbf{Designing for Impact: Conceptualising an Intelligent, Data-Driven Embedded Financial Service}}
% return to normal size
\normalsize

\section*{Problem statement}
\textbf{Target users:} micro-merchants and gig workers selling across marketplaces, delivery platforms, and social channels.\\
\textbf{Financial pain:} volatile daily and weekly cashflows, thin or fragmented credit files, and slow responses from traditional lenders. Liquidity breaks occur due to cashflow mismatches (inventory today, receivables T{+}1/T{+}2), refunds, and operational shocks. Current solutions overweight legacy credit bureau data and paperwork that fail to reflect recent transactional behavior or service quality.\\
\textbf{Context:} users already generate rich operational signals through digital orders, payments, and fulfillment, yet those signals are not orchestrated to decide in real time. The binding constraint is not data scarcity but safe, governed data use in context.\\
\textbf{Need:} an embedded, low-ticket, high-frequency working-capital line with dynamic pricing and optional micro-insurance, delivered in-app with clear consent, instant explanations, and appeal paths.

\section*{Solution overview}
\textbf{Product:} \emph{LumenCash}.\\
\textbf{Value proposition:} embedded working-capital advances plus optional micro-insurance inside non-financial platforms where sellers already operate.\\
\textbf{How it works:} at order confirmation, the system estimates short-term liquidity need and risk using most-recent behavior. It offers a micro-advance (e.g., \$25--\$300) with short tenor (7--28 days), dynamic pricing, and a human-readable rationale. Disbursement lands in the platform wallet; repayment is swept from incoming receivables. Early repayment has no penalty. The optional micro-cover protects bounded operational losses (e.g., damaged goods up to a cap).\\
\textbf{Embedded UX:} no redirects or manual bank transfers. Consent is granular and time-bound via a clear panel. The merchant dashboard shows projected cashflow, expected repayment schedule, marginal cost of the next advance, and inventory hints.\\
\textbf{Outcomes:} inclusion for thin-file users, sub-second decisions, higher order fill-rate, and fewer cash breaks. Platforms gain retention and GMV; competition improves as signals become comparable across providers.\\
\textbf{Safety features:} explainable decisions, adaptive limits, cool-off windows, exposure caps relative to rolling net sales, and alerts that warn before harmful stacking.


\section*{Technology and data}
\textbf{Data:}
\begin{itemize}
  \item \textit{Open data} (public): macro rates and inflation, sector indices, weather and geospatial layers for local risk.
  \item \textit{Private with consent}: bank transactions via AISP, platform events (orders, cancellations, delivery times), device and location signals, user identity via OIDC.
  \item \textit{Blended features}: seasonality, ticket stability, customer concentration, return rates, real-time sales nowcasts.
\end{itemize}
\textbf{AI:} supervised default model for PD (gradient boosting or tabular DL) with time-based splits; time-series nowcasting for demand; anomaly detection for fraud; contextual bandits to select offer size and price. Local explainability (e.g., SHAP) with concise reason codes.\\
\textbf{Platform and standards:} OAuth~2.0 + OIDC with FAPI profile; account aggregation for consented accounts; platform wallet and payouts; event bus for decisions and audit.\\
\textbf{Minimal architecture:} Ingestion $\rightarrow$ Normalisation $\rightarrow$ Feature store $\rightarrow$ Model engine $\rightarrow$ Decision engine $\rightarrow$ Payments orchestration $\rightarrow$ Observability and audit.

\section*{Ethical and governance considerations}
\textbf{Transparency:} decision summaries with key drivers, negative reason codes, confidence ranges, and actionable recourse (e.g., ``increase verified sales consistency for two weeks'' or ``reduce refund ratio below 3\%'').\\
\textbf{Consent:} granular by scope (balances, transactions), per account, with short expiry; immediate revocation; consent receipts stored and viewable.\\
\textbf{Fairness and inclusion:} cohort-level error-parity checks, stability tests, and protected-class monitoring; exposure caps and pricing floors to prevent debt spirals; human-in-the-loop for borderline cases and a formal appeal workflow.\\
\textbf{Privacy and security:} data minimisation, encryption in transit and at rest, short-lived tokens, PAR/JARM/mTLS under FAPI; scope-based segregation; strict retention and scheduled deletion.\\
\textbf{Compliance and accountability:} signed audit logs, drift monitoring, model cards and change control, periodic reviews, risk limits, and kill-switches tied to anomaly thresholds.\\
\textbf{Responsible UX:} no gamification that nudges over-borrowing; healthy friction such as total-cost simulators, salient APR/TaEG disclosure, and clear opt-outs.

\end{document}
